A Process for the Emulation of Comparative Oncology Trials with Real-world Evidence (ENCORE)

### 2024-12-15 manuscript/manuscript.qmd
removed link
added links to higher resolution figures
corrected link

[View figure in higher resolution here](https://github.com/janickweberpals/encore-process-manuscript/blob/main/figures/process.png)

@@

@@

>>>>

[View figure in higher resolution here](https://github.com/janickweberpals/encore-process-manuscript/blob/main/manuscript/Figure_1_process.png)

@@

[View figure in higher resolution here](https://github.com/janickweberpals/encore-process-manuscript/blob/main/manuscript/Figure_2_utlization.png)

@@

[View figure in higher resolution here](https://github.com/janickweberpals/encore-process-manuscript/blob/main/manuscript/Figure_3_balance.png)
